---
title: "Introduction to Binomial"
author: "Rohan Divate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

The package binomial is a package that lets you compute the binomial distribution for a given number of trials, a given probability, and a given number of successes. The binomial package gives a visualization of the distribution in a table and in graph formats.

## Computing probability with the binomial distribution 

If you want to calculate the probability of x number of successes in y number of trials with a probability of success p for each trial, you can do so by using the bin_probability function.

```{r}
bin_probability(4,10,0.5)
```

## Distribution

If you want to compute a binomial distribution with a range of success values, you can use the bin_distribution function. 

```{r}
bin_distribution(trials = 5, prob = 0.5)
```

## Cumulative

You can also get the cumulative distribution of values by using the bin_cumulative function.

```{r}
bin_cumulative(5, 0.5)
```


## Visualizing the distribution

Once you have a binomial distribution using bin_distribution, you can visualize the binomial distribution in a bar graph by using the plot function.

```{r}
bin <- bin_distribution(trials = 5, prob = 0.5)
plot(bin)
```

## Visualizing the cumulative distribution

Once you have a cumulative distribution object using bin_cumulative, you can visualize it by using plot.

```{r}
bin2 <- bin_cumulative(10, 0.2)
plot(bin2)
```

## Binomial Variable Object

You can also work with a binomial variable object using this package. You can create a binvar object by using bin_variable.

```{r}
binv <- bin_variable(10, 0.4)
binv
```


The summary function also gives an output of the different statistics of the distribution.

```{r}
summary(binv)
```

## Functions of measures

Additionally, the package includes different statistic functions that you can use. The functions include the mean, variance, mode, skewness, and kurtosis of a given distribution

```{r}
bin_mean(20, 0.3)
bin_variance(20, 0.3)
bin_mode(20, 0.3)
bin_skewness(20, 0.3)
bin_kurtosis(20, 0.3)
```

